Hardware-Accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-06-24 paper.tex
Switched order of approaches

The first approach uses a Boolean AND operation combined with depth-buffer
masking.  The basic idea is to render the part of the volume directly behind the
intersection, render the intersection itself, and then render the part of the
volume directly in front of the intersection.  Finally the area of the
intersection is masked off and everything else is drawn depth-sorted with
blending enabled.

The first step in this approach is to bind all the textures.  There are two for
the volumes, two for storing the texture coordinates of the back faces of the
cubes, and one for storing results between passes.  The last three textures will
be used with external framebuffers, so they should have a width and height at
least as big as the window.

@@

The second approach uses a Boolean AND operation together with a Boolean XOR.
Here the idea is to break up both volumes into pieces around the intersection.
All the pieces behind the intersection are rendered first, then the intersection
itself, and then all the pieces in front of the intersection.

@@

Like the first approach, the first step is to set up the textures.  There are
two textures for the volumes, two to store the texture coordinates of the back
faces, and one to hold results between passes.  The textures to store the
texture coordinates and results between passes will be used with external
framebuffer objects, and should thus be at least as big as the window.

@@

>>>>

@@

The first approach uses a Boolean AND operation together with a Boolean XOR.
Here the idea is to break up both volumes into pieces around the intersection.
All the pieces behind the intersection are rendered first, then the intersection
itself, and then all the pieces in front of the intersection.

@@

The first step in this approach is to set up the textures.  There are two
textures for the volumes, two to store the texture coordinates of the back
faces, and one to hold results between passes.  The textures to store the
texture coordinates and results between passes will be used with external
framebuffer objects, and should thus be at least as big as the window.

@@

The second approach uses a Boolean AND operation combined with depth-buffer
masking.  The basic idea is to render the part of the volume directly behind the
intersection, render the intersection itself, and then render the part of the
volume directly in front of the intersection.  Finally the area of the
intersection is masked off and everything else is drawn depth-sorted with
blending enabled.

Like the first approach, the first step is to bind all the textures.  There are
two for the volumes, two for storing the texture coordinates of the back faces
of the cubes, and one for storing results between passes.  The last three
textures will be used with external framebuffers, so they should have a width
and height at least as big as the window.
